---
title: "Untitled"
author: "Keisha Rose Harrison"
date: "9/9/2020"
output: html_document
---

Load libraries
```{r}
update.packages()
install.packages("Hmisc")
install.packages("igraph")
install.packages("remotes")
remotes::install_github("heuselm/mocode")
install.packages("GGally")

library(GGally)
library(remotes)
library(backports)
library(Hmisc)
library(dplyr)
library(ape)
library(vegan)
library(corrplot)
library(ggcorrplot)
library(PerformanceAnalytics)
library(igraph)

```
Load data
```{r}
otumat = read.csv("C:/Users/harrikei/Documents/First Paper-Diversity/R Scripts and Data/Diversity/otugenuscorrsmall.csv", sep=",") #OTU table
row.names(otumat) <- otumat$X
otumat <- otumat %>% select (-X)
otu_mat <- as.matrix(otumat)

```


Create correlation data
```{r setup, include=FALSE}
corr <- cor(otu_mat) #Compute a correlation matrix
pmat <- cor_pmat(otumat) #Compute a matrix of correlation p-values

```




This section provides a simple function for formatting a correlation matrix into a table with 4 columns containing :

Column 1 : row names (variable 1 for the correlation test)
Column 2 : column names (variable 2 for the correlation test)
Column 3 : the correlation coefficients
Column 4 : the p-values of the correlations

```{r}

res <- rcorr(as.matrix(otu_mat))

flattenCorrMatrix <- function(corr, pmat) {
  ut <- upper.tri(corr)
  data.frame(
    row = rownames(corr)[row(corr)[ut]],
    column = rownames(corr)[col(corr)[ut]],
    cor  =(corr)[ut],
    p = pmat[ut]
    )
}


corr.mat = flattenCorrMatrix(corr, pmat)
```
write.csv(corr.mat,'corrmatgenus1.csv')


```{r}
# Insignificant correlation are crossed
corrplot(res$r, type="upper", order="hclust", 
         p.mat = res$P, sig.level = 0.05, insig = "blank")
# Insignificant correlations are leaved blank
corrplot(res$r, type="upper", order="hclust", 
         p.mat = res2$P, sig.level = 0.01, insig = "blank")

ggcorr(res$r, nbreaks= 5, ggtheme = ggplot2::theme_gray, colors = c("#6D9EC1", "white", "#E46726"), label=FALSE, label_size=4, tl.cex=2, label_color='black', layout.exp=5, angle = 1,  hjust = 0.99) 
```
ggcorr(res$r, nbreaks= 5, ggtheme = ggplot2::theme_gray, colors = c("#E46726", "white","#6D9EC1"), label=FALSE, label_size=4, tl.cex=2, label_color='black', layout.exp=5, angle = 1,  hjust = 0.99, legend.size=10, tl.cex = 1.5, cl.cex = 1.5) 


```{r}

{plot.new(); dev.off()}
corrplot(res$r)

{plot.new(); dev.off()} 
corrplot(res$r,title = "Correlation Plot", method = "square", outline = T, addgrid.col = "darkgray", order="hclust", mar = c(4,0,4,0), addrect = 4, rect.col = "black", rect.lwd = 5,cl.pos = "b", tl.col = "indianred4", tl.cex = 1.5, cl.cex = 1.5, type = "upper")

```

```{r}
#o obtain the p-value information from the list, use otu.cor$P, using the function forceSymmetric() to assign self-correlation as NA
otu.pval = forceSymmetric(res$P)
```


```{r}
p.yes <- res$P<0.05

r.val = res$r>0.2 # select all the correlation values 
p.yes.r <- r.val*p.yes # only select correlation values based on p-value criterion 
p.yes.r <- abs(p.yes.r)>0.2 # output is logical vector
p.yes.rr <- p.yes.r*r.val # use logical vector for subscripting.
adjm <- as.matrix(p.yes.rr)
```


```{r}
net.grph=graph.adjacency(adjm,mode="undirected",weighted=TRUE,diag=FALSE)
edgew<-E(net.grph)$weight
V(net.grph)$color <- tax$Phylum
bad.vs<-V(net.grph)[degree(net.grph) == 0] 
net.grph <-delete.vertices(net.grph, bad.vs)
```



```{r}
plot(net.grph,
 vertex.size=8,
 vertex.frame.color="black",
 edge.curved=F,
 edge.width=edgew,
 layout=layout.fruchterman.reingold,
 edge.color=ifelse(edgew > 1,"red","blue"),
 vertex.label=NA,
 vertex.label.color="black",
 vertex.label.family="Times New Roman",
 vertex.label.font=0.1)

```

```{r}

```

