---
title: "Phyloseq Rundown"
output: pdf_document
author: Keisha Harrison
date: 03/05/20
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load libraries
```{r}
install_github("pmartinezarbizu/pairwiseAdonis/pairwiseAdonis")
install.packages("remotes")
remotes::install_github("leffj/mctoolsr")

library(stringi)
library(phyloseq)
library(ggplot2)
library(dplyr)
library(ape)
library(S4Vectors)
library(vegan)
library(DESeq2)
library(agricolae)
library(devtools)
library(pairwiseAdonis)
library(xlsx)
theme_set(theme_bw())


source("https://bioconductor.org/biocLite.R")
biocLite("GenomeInfoDbData")

```

#load data
```{r}

##load data csv files
otumat = read.csv("C:/Users/harrikei/Documents/First Paper-Diversity/R Scripts and Data/Diversity/phyloseq/otumat3.csv", sep=",") #OTU table
taxmat = read.csv("C:/Users/harrikei/Documents/First Paper-Diversity/R Scripts and Data/Diversity/phyloseq/taxmat.csv", sep = ",") #Taxa information
meta = read.csv("C:/Users/harrikei/Documents/First Paper-Diversity/R Scripts and Data/Diversity/phyloseq/metamat3.csv", sep = ",") #Meta data

#Set sample names and meta data labels so that we can call upon groups, ect
row.names(otumat) <- otumat$X
otumat <- otumat %>% select (-X) 

row.names(taxmat) <- taxmat$X
tax_mat <- taxmat %>% select (-X) 

row.names(meta) <- meta$sample 
samples_df <- meta %>% select (-sample) 


# Convert OTU and taxa data frames into matrices to be compatible with phyloseq package
otu_mat <- as.matrix(otumat)
tax_mat <- as.matrix(taxmat)

```


#Construct phyloseq model 
```{r}
#load OTU data and taxonomy data into phyloseq model
OTU = otu_table(otu_mat, taxa_are_rows = TRUE)
TAX = tax_table(tax_mat)
samples = sample_data(samples_df)
samples

#merge phyloseq model
carbom <- phyloseq(OTU, TAX, samples)
carbom

#make phylo tree
random_tree = rtree(ntaxa(carbom), rooted=TRUE, tip.label=taxa_names(carbom))

sample_names(carbom)
sample_variables(carbom)

#Model now includes meta data, sample variables, OTU labels, OTU abundance, and random tree
carbom = merge_phyloseq(carbom, random_tree)

```

#Construct bargraphs
```{r}
plot_bar(carbom, fill="Taxa")
plot_bar(carbom, fill="Taxa") + facet_wrap(~Cluster, scales= "free_x", nrow=1)

#without wrap
#plot_bar(carbom, fill="Genus")

```


#Alpha diversity
```{r}

otu_table(carbom) <- otu_table(round(as((otu_table(carbom)), "matrix")), taxa_are_rows(carbom))
rich = estimate_richness(carbom)
alpha = estimate_richness(carbom, measures=c(samples, "Observed", "InvSimpson", "Shannon", "Chao1", "Simpson", samples))

write.xlsx(alpha, "alphadiversy3.xlsx")
plot_richness(carbom, measures=c("Simpson", "Shannon", "InvSimpson"))

names = rownames(alpha)
print(names)

plot_richness(carbom, x="Cluster", measures=c("Simpson", "InvSimpson", "Observed")) + geom_boxplot() +  theme(text = element_text(size = 20))
#ANOVA- alpha
adonis(alpha$Simpson ~ sample_data(carbom)$Cluster)

```

#Beta-diversity/PCoA and ANOVA
```{r}

unifrac_dist = phyloseq::distance(carbom, method="unifrac", weighted=T)
ordination <- ordinate(carbom, "PCoA", "unifrac", weighted = TRUE)
ordinationu <- ordinate(carbom, "PCoA", "unifrac", weighted = FALSE)


#Cluster-Diversity
plot_ordination(carbom, ordination, color="Cluster") + theme(aspect.ratio=1) + theme(text = element_text(size = 20)) + stat_ellipse(geom = "polygon", aes(fill = Cluster), type = "norm", level = .9, alpha = 0.1)


adonis(unifrac_dist ~ sample_data(carbom)$Origin)
adonis(unifrac_dist ~ sample_data(carbom)$Cluster)
adonis(unifrac_dist ~ sample_data(carbom)$Batch)
adonis(unifrac_dist ~ sample_data(carbom)$Unique)

#Location-Layer
plot_ordination(carbom, ordination, color="Layer") + theme(aspect.ratio=1) + theme(text = element_text(size = 20)) + stat_ellipse(geom = "polygon", type = "norm", level = .8, alpha = 0.1)
adonis(unifrac_dist ~ sample_data(carbom)$Layer)
pairwise.adonis2(ordination ~ sample_data(carbom)$Layer)

#Layer-Layer
plot_ordination(carbom, ordination, color="Layer") + theme(aspect.ratio=2)
adonis(wunifrac_dist ~ sam_data(carbom)$Layer)

plot_ordination(carbom, carbom.ord, type="taxa", color="Genus", shape= "Family", 
                title="OTUs")

```



Weighed Unifrac- PCoA
```{r}
ordplot = plot_ordination(carbom, ordination, color="Layer", title="PCoA - Unifrac") + theme(aspect.ratio=1)
ordplot + stat_ellipse(geom = "polygon", type = "norm", alpha = 0.15, aes(fill = Layer)) + theme(text = element_text(size = 30)) 


```

Unweighed Unifrac- PCoA
```{r}
ordplotu = plot_ordination(carbom, ordinationu, color="Cluster", title="PCoA - Unweighed Unifrac") + theme(aspect.ratio=1)
ordplotu + stat_ellipse(geom = "polygon", type = "norm", alpha = 0.2, aes(fill = Cluster))


```


